---
title: "3D Design and Practical Projects"
---

\

```{r, setup, echo=FALSE, message = FALSE, warning=FALSE}
options(rgl.useNULL = TRUE) # Suppress the separate window.
library(rgl)
library(embedr)
```

# Flightmill for measuring insect flight behaviours

A multi-chambered mill that uses a Raspberry pi configured as a data-logger. This set-up records data from optical sensors that are triggered by the rotation of arms to which burying beetles are mounted. The aim is to monitor the activity of beetles mounted in each chamber for several hours at a time.

``` {=html}
<video controls loop>
  <source src="images/flightmill_video.mp4" type="video/mp4">
Your browser does not support the video tag.
</video>
```

\

------

\

# Screen Case for a Pi 2B

This project is for a smart clock built with a Raspberry Pi 2B and a [3.5" touchscreen](http://www.lcdwiki.com/3.5inch_RPi_Display). This case has three parts (base, lid, and stand) that I designed in FreeCAD 0.21.0. The most basic implementation idea is to have a dedicated display for local bus times and weather updates. Ultimately, it would be fun to tie in some sensors running on a Pi Pico W or Pi Zero 2W to report on conditions in the home or lab. Programming notes to follow.

```{r, echo=FALSE, message = FALSE, warning=FALSE}
# Read the .obj file
obj_file <- readOBJ("images/case_base_lid_stand.obj", 
                    material = list(color = "darkgrey", specular = "black"))
# initialise a plot space with no text update
open3d(silent = T)

# plot object
shade3d(obj_file)
bg3d(color = "lightgrey")  # set background as grey, makes manipulating object easier
rglwidget()
```

\

------

\

# Tower Case for a Pi 4B

This project was intended to tackle some cooling issues I was having with the Raspberry Pi 4B, hence the top and rear rails for 40mm fans. Both side panels are removable, one on a slide system, the other with screws. The case includes space underneath the main Pi board for a [2-cell UPS board](https://thepihut.com/products/uninterruptible-power-supply-ups-hat-b-for-raspberry-pi), a power switch, and a mini OLED screen for system status updates.

```{r, echo=FALSE, message = FALSE, warning=FALSE, fig.align = 'center'}
# Read the .obj file
obj_file <- readOBJ("images/pi_tower_case.obj", material = list(color = "darkgrey"))
# initialise a plot space with no text update
open3d(silent = T) 

# plot object
shade3d(obj_file, specular = "black", color = "darkgrey")
bg3d("lightgrey")  # set background as grey, makes manipulating object easier

rglwidget()
```

\

------

\


# Wind-tunnel case for Pi Zero

This is a small case for the Raspberry Pi Zero or Zero 2W. It runs a 40mm fan on the left, blowing across the main board. This is overkill for cooling, but very cute and satisfying. The front panel is a slide, giving access to GPIO pins if necessary. Otherwise, this is a great case for safely running a tiny Pi board as a mini PC.

```{r, echo=FALSE, message = FALSE, warning=FALSE, fig.align = 'center'}
# Read the .obj file
obj_file <- readOBJ("images/pi_zero_case_v3.1.obj", material = list(color = "darkgrey"))
# initialise a plot space with no text update
open3d(silent = T) 

# plot object
shade3d(obj_file, specular = "black", color = "darkgrey")
bg3d("lightgrey")  # set background as grey, makes manipulating object easier

rglwidget()
```


\

------

\


# Coffee Grinder Stand

A simple stand for the [Hario Skerton](https://www.hario.co.uk/products/hario-skerton-plus-ceramic-coffee-grinder) coffee grinder. This just solved a problem in my kitchen where the top of the grinder kept falling over and everything looked messy. The grinder sits into the raised column and the base jar sits in the raised bed.

```{r, echo=FALSE, message = FALSE, warning=FALSE, fig.align = 'center'}
# Read the .obj file
obj_file <- readOBJ("images/coffee_grinder_stand.obj", material = list(color = "darkgrey"))
# initialise a plot space with no text update
open3d(silent = T) 

# plot object
shade3d(obj_file, specular = "black", color = "darkgrey")
bg3d("lightgrey")  # set background as grey, makes manipulating object easier

rglwidget()
```

